---
title: "MA678 Homework 4"
author: "Jiun Lee"
date: "10/4/2022"
output: pdf_document
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(rstanarm)
library(ggplot2)
library(arm)
```

## 13.5 Interpreting logistic regression coefficients

Here is a fitted model from the Bangladesh analysis predicting whether a person with high-arsenic drinking water will switch wells, given the arsenic level in their existing well and the distance to the nearest safe well:

    stan_glm(formula = switch ~ dist100 + arsenic, family=binomial(link="logit"), data=wells)  
                 Median MAD_SD  
    (Intercept)   0.00   0.08  
    dist100      -0.90   0.10  
    arsenic       0.46   0.04  

Compare two people who live the same distance from the nearest well but whose arsenic levels differ, with one person having an arsenic level of 0.5 and the other person having a level of 1.0. You will estimate how much more likely this second person is to switch wells. Give an approximate estimate, standard error, 50% interval, and 95% interval, using two different methods:

### (a)

Use the divide-by-4 rule, based on the information from this regression output.

Answer)

The slope of the curve is maximized at the point when the slope is B/4. From the model above, Pr(switch) = logit^-1(-0.90 * dist100 + 0.46*arsenic), we can divide 0.46 by 4 to get a difference of 1 unit in arsenic level.

0.46 /4 = 0.115

It corresponds to no more than an 11.5% positive difference in the probability of switching wells. Therefore, the second person who has more arsenic level will more likely to switch the sells no more than 11.5%.

### (b)

Use predictive simulation from the fitted model in R, under the assumption that these two people each live 50 meters from the nearest safe well.r

```{r}
set.seed = 145
data_wells <- read.csv("/Users/jiunlee/MSSP22/MA678/ROS-Examples-master/Arsenic/data/wells.csv")
fit_135 <- stan_glm(formula = switch ~ dist100 + arsenic, family=binomial(link="logit"), data=data_wells, refresh=0)
data1 <- data.frame(dist100 = c(0.5,0.5), arsenic=c(0.5,1))
prediction <- posterior_epred(fit_135, newdata=data1)  #p=inversed logit
print(c(mean(prediction), sd(prediction)))
#sqrt(diag(vcov(fit_135)))


quantile(invlogit(data_wells$dist100*0.5+data_wells$arsenic)-invlogit(data_wells$dist100*0.5+wells$arsenic*0.5),c(0.25,0.75))

quantile(invlogit(data_wells$dist100*0.5+data_wells$arsenic)-invlogit(data_wells$dist100*0.5+data_wells$arsenic*0.5),c(0.025,0.975))

```

## 13.7 Graphing a fitted logistic regression

We downloaded data with weight (in pounds) and age (in years) from a random sample of American adults. We then defined a new variable:

    heavy <- weight > 200

and fit a logistic regression, predicting heavy from `height` (in inches):

    stan_glm(formula = heavy ~ height, family=binomial(link="logit"), data=health)  
                  Median MAD_SD  
    (Intercept)  -21.51   1.60  
    height         0.28   0.02  

### (a)

Graph the logistic regression curve (the probability that someone is heavy) over the approximate range of the data. Be clear where the line goes through the 50% probability point.

```{r}
curve(invlogit(-21.51 + 0.28*x), xlim = c(40,110), xlab = "Height (in.)", ylab = "Probability of being heavy")
```

### (b)

Fill in the blank: near the 50% point, comparing two people who differ by one inch in height, you'll expect a difference of 7% in the probability of being heavy.

## 13.8 Linear transformations

In the regression from the previous exercise, suppose you replaced height in inches by height in centimeters. What would then be the intercept and slope?

Answer) 1 inch= 2.54cm,

log(odds)= -21.51 + 0.28 * x -> -21.51 + 0.28 * 2.54 *x

The intercept doesn't change, but the slope changes 0.07 to 0.71.

## 13.10 Expressing a comparison of proportions as a logistic regression

A randomized experiment is performed within a survey, and 1000 people are contacted. Half the people contacted are promised a $5 incentive to participate, and half are not promised an incentive. The result is a 50% response rate among the treated group and 40% response rate among the control group.

### (a)

Set up these results as data in R. From these data, fit a logistic regression of response on the treatment indicator.

```{r}
set.seed=321
incen <- c(rep(1,500), rep(0,500))
resp <- c(rep(1,200),rep(0,300),rep(1,250),rep(0,250))
data_resp <- data.frame(incen,resp)
fit_131 <- stan_glm(resp~incen, family=binomial(link="logit"), data=data_resp, refresh=0)

```

### (b)

Compare to the results from Exercise 4.1(Give an estimate and standard error of the average treatment effect.).

```{r}
summary(fit_131,digits=3)

#exercise4.1
set.seed = 111
fit_131b <- lm(resp~incen, data=data_resp)
summary(fit_131b)

#The results of both exercises are similar.

```

## 13.11 Building a logistic regression model

The folder `Rodents` contains data on rodents in a sample of New York City apartments.

### (a)

Build a logistic regression model to predict the presence of rodents (the variable `rodent2` in the dataset) given indicators for the ethnic groups (`race`). Combine categories as appropriate. Discuss the estimated coefficients in the model.

```{r}
set.seed=243
data_rod <- read.table("/Users/jiunlee/MSSP22/MA678/ROS-Examples-master/Rodents/rodents.dat")
fit_rod <- stan_glm(rodent2~race, family=binomial(link="logit"), data=data_rod,refresh=0)
summary(fit_rod, digits=3)

# When the race increases by 1 unit, the odds of the presence of rodents increase by 1.306 times. (since,exp(0.305)=1.306);that is,  the odds of the presence of rodents are increased by 30.6% when the race is black(race=2) than when the race is white(race=1).

```

### (b)

Add to your model some other potentially relevant predictors describing the apartment, building, and community district. Build your model using the general principles explained in Section 12.6. Discuss the coefficients for the ethnicity indicators in your model.

```{r}
set.seed=122
fit_rod2 <- stan_glm(rodent2~race+stories+dilap+old_Mean, family=binomial(link="logit"), data=data_rod,refresh=0)
summary(fit_rod2,digits=3)

# When the race increases by 1 unit, the odds of the presence of rodents increase by 1.35 times. (since,exp(0.299)=1.35);that is,  the odds of the presence of rodents are increased by 35% when the race is black(race=2) than when the race is white(race=1).

```

## 14.3 Graphing logistic regressions

The well-switching data described in Section 13.7 are in the folder `Arsenic`.

### (a)

Fit a logistic regression for the probability of switching using log (distance to nearest safe well) as a predictor.

```{r}
set.seed = 125
data_wells <- read.csv("/Users/jiunlee/MSSP22/MA678/ROS-Examples-master/Arsenic/data/wells.csv")
data_wells$logdist <- log(data_wells$dist)
fit_143 <- stan_glm(formula = switch ~ logdist + arsenic, family=binomial(link="logit"), data=data_wells, refresh=0)

```

### (b)

Make a graph similar to Figure 13.8b displaying Pr(switch) as a function of distance to nearest safe well, along with the data.

```{r}
newdata143 <- data.frame(logdist=data_wells$logdist,arsenic=data_wells$arsenic)
newdata143$switch <- predict(fit_143,newdata=newdata143,type="response")

ggplot(data_wells, aes(x=logdist, y=switch)) + 
  geom_point(size=0.1)+
  stat_smooth(method="glm", se=FALSE, method.args = list(family=binomial),col="red", lty=2)
```

### (c)

Make a residual plot and binned residual plot as in Figure 14.8.

```{r}
#Residual Plot
res <- resid(fit_143)
plot(fitted(fit_143), res, main = "Residual Plot",xlab="Estimated Pr (switching)",ylab  = "Observed - estimated")
abline(0,0)

#Binned Residual Plot
binnedplot(x=fitted(fit_143),y=res,main="Binned Residual Plot", xlab="Estimated Pr(Switching)", ylab="Average Residual")
```

### (d)

Compute the error rate of the fitted model and compare to the error rate of the null model.

```{r}
prediction <- fitted(fit_143)
error_rate <- mean((prediction>0.5 & wells$switch==0) | (prediction<0.5 & wells$switch==1))

error_null <- sum(data_wells$switch)/3020

#The null model has an error rate of 58%, so 42% of the respondents are switchers and 58% are not, thus the model with no predictors gives each person a 42% chance of switching.

#The error rate is 38%. This model predict the behavior of 62% of the respondents in the data correctly.

```

### (e)

Create indicator variables corresponding to `dist < 100`; `dist` between 100 and 200; and `dist > 200`. Fit a logistic regression for Pr(switch) using these indicators. With this new model, repeat the computations and graphs for part (a) of this exercise.

```{r}
#dist<100:group=1,100<=dist&dist<=200:group=2, dist>200: group=3
data_wells$group <- as.factor(ifelse(data_wells$dist<100,1,
                              ifelse(data_wells$dist>=100 & 
                                     data_wells$dist<=200,2,3)))
set.seed=490
fit_143e <- stan_glm(switch ~ logdist + arsenic + group,family=binomial(link="logit"), data=data_wells, refresh=0)

newdata143e <- data.frame(logdist=data_wells$logdist,arsenic=data_wells$arsenic,group=data_wells$group)
newdata143e$switch <- predict(fit_143e,newdata=newdata143e,type="response")

ggplot(data_wells, aes(x=logdist, y=switch,color=group))+
  geom_point(size=0.2)+
  stat_smooth(method="glm",se=FALSE, method.args = list(family=binomial),col="blue")
```

## 14.7 Model building and comparison

Continue with the well-switching data described in the previous exercise.

### (a)

Fit a logistic regression for the probability of switching using, as predictors, distance, log(arsenic), and their interaction. Interpret the estimated coefficients and their standard errors.

```{r}
set.seed = 324
data_wells$log_ars <- log(data_wells$arsenic)
fit_147 <- stan_glm(formula = switch ~ dist100 + log_ars + dist100:log_ars, family=binomial(link="logit"), data=data_wells, refresh=0)

# The intercept(0.5) would correspond to the log odds of switching for a student with average distance, average level of arsenic.
# With one unit increase in dist100, it leads to a multiplicative effect of exp(-0.9)*exp(-0.2) on the expected odds of switch. So,the odds of switch will be increased by 0.33times.(since, exp(-0.9)*exp(-0.2)=0.33)

# With one unit increase in log_ars, it leads to a multiplicative effect of exp(1.0)*exp(-0.2) on the expected odds of switch. Therefore, the odds of switch will be decreased by 2.23times (since, exp(1.0)*exp(-0.2)=2.23)


```

### (b)

Make graphs as in Figure 14.3 to show the relation between probability of switching, distance, and arsenic level.

```{r}
set.seed=99
fit_147b <- stan_glm(switch ~ dist100 + arsenic, family = binomial(link = "logit"),data=data_wells, algorithm='optimizing',refresh=0)
jitter_binary <- function(a, jitt=.05){
  a + (1-2*a)*runif(length(a),0,jitt)
}
plot(c(0,max(data_wells$dist,na.rm=T)*1.02), c(0,1),
     xlab="Distance (in meters) to nearest safe well", ylab="Pr (switching)",
     type="n", xaxs="i", yaxs="i", mgp=c(2,.5,0))
points(data_wells$dist, jitter_binary(data_wells$switch), pch=20, cex=.1)
curve(invlogit(coef(fit_147b)[1]+coef(fit_147b)[2]*x/100+coef(fit_147b)[3]*.50), lwd=.5, add=T)
curve(invlogit(coef(fit_147b)[1]+coef(fit_147b)[2]*x/100+coef(fit_147b)[3]*1.00), lwd=.5, add=T)
text(50, .27, "if As = 0.5", adj=0, cex=.8)
text(75, .50, "if As = 1.0", adj=0, cex=.8)


```

### (c)

Following the procedure described in Section 14.4, compute the average predictive differences corresponding to:

i.  A comparison of `dist` = 0 to `dist` = 100, with `arsenic` held constant.\
ii. A comparison of `dist` = 100 to `dist` = 200, with `arsenic` held constant.\
iii. A comparison of `arsenic` = 0.5 to `arsenic` = 1.0, with `dist` held constant.\
iv. A comparison of `arsenic` = 1.0 to `arsenic` = 2.0, with `dist` held constant.

Discuss these results.

```{r}
#i
b <- coef(fit_147b)
hi <- 1 #dist=100->dist100=1
lo <- 0 #dist=0->dist=0
delta1 <- invlogit(b[1] + b[2]*hi + b[3]*data_wells$arsenic) -
invlogit(b[1] + b[2]*lo + b[3]*data_wells$arsenic)
round(mean(delta1), 2)
#The result is -0.21.This comparison corresponds to a 21% difference in probability of switching.


#ii
hi <- 2 #dist=200->dist100=2
lo <- 1 #dist=100->dist=1
delta2 <- invlogit(b[1] + b[2]*hi + b[3]*data_wells$arsenic) -
invlogit(b[1] + b[2]*lo + b[3]*data_wells$arsenic)
round(mean(delta2), 2)
#The result is -0.19.This comparison corresponds to a 19% difference in probability of switching.


#iii
a1 <- 1.0
a0 <- 0.5
delta3 <- invlogit(b[1] + b[2]*data_wells$dist100 + b[3]*a1) -
invlogit(b[1] + b[2]*data_wells$dist100 + b[3]*a0)
round(mean(delta3), 2)
#The result is 0.06. This comparison corresponds to a 6% difference in probability of switching.

#iv
a1 <- 2.0
a0 <- 1.0
delta4 <- invlogit(b[1] + b[2]*data_wells$dist100 + b[3]*a1) -
invlogit(b[1] + b[2]*data_wells$dist100 + b[3]*a0)
round(mean(delta4), 2)
#The result is 0.11. This comparison corresponds to a 11% difference in probability of switching.
```
